%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {co-owner \& CTO} % Job title
    {Empresas Moux-Orcasita LLC} % Organization
    {San Juan, Puerto Rico} % Location
    {Jan. 2016 - current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
	    \item {Bootstrapping businesses, creating technology for ventures, and consulting.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
	{Senior Software Developer \& Programmer} % Job title
	{Great Bay Global LLC (previously known as Great Bay Energy)} % Organization
    {San Juan, Puerto Rico} % Location
    {Jan. 2014 - Mar. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
		\item{Produced many analysis tools, systems and ETLs for traders that enabled revenue generation.}
	  \item {Generated profits in the millions (within 6 months) via own and co-managed portfolios (30+, PJM \& ERCOT).}
		\item{Produced an improved version of an existing trade mining system (410\% in time-to-completion, from week to hours).}
		\item{Decreased deployment pullbacks by an order of magnitude by introducing agile + lean methodologies \& best practices.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Developer} % Job title
    {OSIsoft, LLC} % Organization
    {San Leandro, California} % Location
    {Sep. 2008 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
		\item{Built the BI project that support management uses to make decisions and improve qualitive of service.}
	    \item{Contributed to central projects (\href{http://www.osisoft.com/software-support/ea/Managed_PI.aspx}{mPI} \& Pipeline) that generate millions in revenue and on which the company bets its future.}
		\item{Resolved over 1,600 support cases (11th/100s most productive volume-wise, in Spanish \& English) across various industries.}
		\item{Ran scale tests for the C. Advisory Service's Advanced Metering Infrastructure initiative and improved existing throughput by 25\%.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research assistant / Graduate student} % Job title
    {Molecular Thermodynamics lab} % Organization
    {Madison, Wisconsin} % Location
    {Sep. 2006 - Mar. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
		  \item {Analyzed phase transitions of liquid crystals via atomistic molecular dynamics and Monte Carlo (own code).}
      \end{cvitems}
    }


\end{cventries}

